Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-18 doc/PRF2022/PRF_main.tex
fixed up BIE section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We require a method to accurately solve the Stokes and screened Laplace
equations in intricate, unbounded geometries.  This is done by
recasting~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretizing each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double-layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
    \xx \in \partial \Omega.
\end{align}

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES
and the second-kind BIEs
guarantee that the number of GMRES iterations is
mesh-independent.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We require a method to accurately solve the Stokes and screened Laplace
equations in intricate, unbounded geometries.  This is done by
recasting~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretizing each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double-layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution of the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\eta$ is a scalar-valued density
function. The subscript in $\dif s_\yy$ denotes integration with respect
to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must
satisfy~\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
    \xx \in \partial \Omega.
\end{align}

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $(2N+3)N_b \times (2N+3)N_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES and the second-kind BIEs
guarantee that the number of GMRES iterations is mesh-independent.
